Study protocol

### 2021-08-19 Manuscript/S1.Protocol.Rmd
some formatting fix

---
title: "Study protocol"
date: "`r lubridate::today()`"
output:
  github_document:
    html_preview: false
    toc: yes
---

@@

```{r perform searches}
# This call will perform an API search on Pubmed, WOS and IEEE services and/or
# (based on the `actions` argument) parse already downloaded data (in our case, additional Pubmed results and Embase and Scopus results) manually added to the Session1/Query1 folder.
journal <- perform_search_session(
	query = query, year_query = year_filter,
	session_name = 'Session1', query_name = 'Query1',
	records_folder = 'Records',
	journal = 'Session_journal.csv')

@@

# The last annotation file and posterior sample matrix in the session are
# found; the most predictive terms (based on the importance score) are chosen
# and simple prediction trees are used to map the terms to a random subset of
# the posterior probabilities (extracted from the posterior sample matrix saved
# during the last CR iteration). The score threshold and the number of trees can be
# chosen by the user; less stringent values can greatly increase computation
# time;

@@

$$
Sensitivity \times Efficiency = \\
\frac{Pos.\ found}{Tot.\ pos.} \times \frac{Records\ reviewed}{Tot.\ records}
$$
We added a tools to the framework to find a set of hyperparameters using by a "grid search" algorithm. We tested these tools on our dataset, manually labeling the first 1200 records, ordered by simple query match.\
The first step is to create a folder where to store the file required for the search, for example *Grid Search*. Then a fully reviewed records file in the format generated by `create_annotation_file()` is necessary; this file can be put in the *Grid Search* but it is not mandatory. Once the folder and the file are ready run:

```{r grid search}
Grid_search <- perform_grid_evaluation(records, sessions_folder = 'Grid_Search',
																			 prev_classification = records,
																			 ## Model parameters, deg
																			 resample = c(FALSE, TRUE),
																			 n_init = c(50, 100, 250, 500),
																			 n_models = c(5, 10, 20, 40, 60),
																			 pos_mult = c(1, 10, 20),
																			 pred_quants = list(c(.1, .5, .9),
																			 									 c(.05, .5, .95),
																			 									 c(.01, .5, .99))
)
```

>>>>

---
title: "Study protocol"
date: "`r lubridate::today()`"
output:
  github_document:
    toc: yes
---

@@

```{r perform searches}
# This call will perform an API search on Pubmed, WOS and IEEE services and/or
# (based on the `actions` argument) parse already downloaded data (in our case,
# additional Pubmed results and Embase and Scopus results) manually added to the
# Session1/Query1 folder.

journal <- perform_search_session(
	query = query, year_query = year_filter,
	session_name = 'Session1', query_name = 'Query1',
	records_folder = 'Records',
	journal = 'Session_journal.csv')

@@

# The last annotation file and posterior sample matrix in the session are found;
# the most predictive terms (based on the importance score) are chosen and
# simple prediction trees are used to map the terms to a random subset of the
# posterior probabilities (extracted from the posterior sample matrix saved
# during the last CR iteration). The score threshold and the number of trees can
# be chosen by the user; less stringent values can greatly increase computation
# time;

@@

$$
Sensitivity \times Efficiency = \\
\frac{Pos.\ found}{Tot.\ pos.} \times \frac{Records\ reviewed}{Tot.\ records}
$$
We added a tool that uses a “grid search” algorithm to find the best set of hyperparameters. We tested these tools on our dataset, manually labeling the first 1200 records, ordered by simple query match.\
The first step is to create a folder where to store the file required for the search, for example *Grid Search*. Then a fully reviewed records file in the format generated by `create_annotation_file()` is necessary; this file can be put in the *Grid Search* but it is not mandatory. Once the folder and the file are ready run:

```{r grid search}
Grid_search <- perform_grid_evaluation(
	records, sessions_folder = 'Grid_Search',
	prev_classification = records,
	## Model parameters
	resample = c(FALSE, TRUE),
	n_init = c(50, 100, 250, 500),
	n_models = c(5, 10, 20, 40, 60),
	pos_mult = c(1, 10, 20),
	pred_quants = list(
		c(.1, .5, .9),
		c(.05, .5, .95),
		c(.01, .5, .99))
)
```
